Citation Analysis of Computer Science Publications

### 2019-12-06 Scientometrics/comp.tex
updated ar_cp figure

 \begin{figure}[ht]
\centering
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[scale=0.5]{ar_cp_ratio.pdf}
% figure caption is below the figure
\caption{Summary of DBLP data cross-matched with Scopus. 2,685,356 publications from DBLP were cross-matched with Scopus and then grouped by the 27 major subject areas in the ASJC (Scopus) classification. The largest number of publications are contributed by Computer Science; Mathematics; and Engineering and then by Social Sciences; Physics and Astronomy; and Biochemistry, Genetics, and Molecular Biology. Publications were further annotated with respect to being either articles \emph{(ar)} or conference proceedings \emph{(cp)}. For this dataset, the major subject areas of Computer Science (2,059,120 (cp), 1,576,691 (ar); Engineering; and Mathematics contributed the most publications while Pharmacology, Toxicology, and Pharmaceutics; Nursing, Veterinary and Dentistry (1 ar) contributed the least.}
\label{fig:ar_cp_annotation}       % Give a unique label
\end{figure}

>>>>

 \begin{figure}[ht]
\centering
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[scale=0.5]{ar_cp_ratio.pdf}
% figure caption is below the figure
\caption{Summary of DBLP data cross-matched with Scopus. 2,685,356 publications from DBLP were cross-matched with Scopus and then grouped by the 27 major subject areas in the ASJC (Scopus) classification. The largest number of publications are contributed by Computer Science; Mathematics; and Engineering and then by Social Sciences; Physics and Astronomy; and Biochemistry, Genetics, and Molecular Biology. Publications were further annotated with respect to being either articles \emph{(ar)} or conference proceedings \emph{(cp)}. For this dataset, the major subject area of Computer Science (1,194,623(cp), 879,396 (ar) contributed the most publications while Nursing (69 cp,  756 ar) contributed the least.}
\label{fig:ar_cp_annotation}       % Give a unique label
\end{figure}
